Bayes network classifiers for fMRI

### 2012-10-16 article/article.tex

- basic terms introduced (fmri, classification, ...)
- related work and results
- briefly build up to state of the art, mention methods we tried?
- state of the art: multivariate pattern analysis (\cite{Haxby2012852})

@@

- classification problem
- prediction
- cognitive state
\section{Methods}
\label{sec:methods}
- comparison
- classifying subtrials vs trials (ie 54 vs 27)
- analysis / tools (python etc)

@@

\subsection{Feature selection}
%Inspired by: http://www.brainvoyager.com/bvqx/doc/UsersGuide/WebHelp/Content/MVPATools/MVPA_Basic_Concepts.htm
Typical input for the machine learning algorithms discussed in this paper consists of a number of feature vectors, one for each fMRI scan. Such a feature vector $\vec{x}$ contains measures for the $N$ features we use to represent that scan and is derived from our input data. In the most basic case, we could use the entire set of voxels belonging to a scan, resulting in a feature vector containing potentially (hundreds of) thousands of features.
In the case that we have a very large dimension of features combined with only a limited amount of scans, our classifier may have difficulty learning the right classification function. This problem is formally known as the \textit{Hughes effect}\cite{Hughes1054102} which states that the predictive power of a machine learning algorithm decreases as the dimensionality increases with a fixed number of training examples.

@@

- same for each algorithm:
    - supervised learning
        - feature selection
            - ROI vs Whole Brain
        - classification / discrimination / scoring function
    - naive bayes
    - multivariate
    - multi-voxel pattern analysis
    - pca

>>>>

- basic terms introduced (fmri, classification, ...)
- related work and results
- briefly build up to state of the art, mention methods we tried?
- state of the art: probably multivariate pattern analysis! (\cite{Haxby2012852})

@@

- classification problem
- prediction
- cognitive state
\section{Methods}
\label{sec:methods}
General approach consisting of three steps, plus basic data acquisition and preprocessing.
\begin{enumerate}
  \item Feature selection
  \item Training
  \item Testing
\end{enumerate}

- comparison
- classifying subtrials vs trials (ie 54 vs 27)
- analysis / tools (python etc)

@@

\subsection{Feature selection}
%Useful background info: http://www.brainvoyager.com/bvqx/doc/UsersGuide/WebHelp/Content/MVPATools/MVPA_Basic_Concepts.htm
Typical input for the machine learning algorithms discussed in this paper consists of a number of feature vectors, one for each fMRI scan. Such a feature vector $\vec{x}$ contains measures for the $N$ features we use to represent that scan and is derived from our input data. In the most basic case, we could use the entire set of voxels belonging to a scan, resulting in a feature vector containing potentially (hundreds of) thousands of features.
In the case that we have a very large dimension of features combined with only a limited amount of scans, our classifier may have difficulty learning the right classification function. This problem is formally known as the \textit{Hughes effect}\cite{Hughes1054102} which states that the predictive power of a machine learning algorithm decreases as the dimensionality increases with a fixed number of training examples.

@@

- same for each algorithm:
    - What features did we select?
    - How did we train?
    - How did we test?
        - How did we calculate performance?
- algorithms:
    - gaussian naive-bayes (gnb)
        - pca + gnb
    - multivariate
    - svm
